Data Deduplication and Zipf-like Distribution in VM Cloud Storage

### 2012-03-01 vm_snapshot_sim/2012intro.tex

Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
virtual disk image backup and even each virtual disk is viewed as a file logically, its size is very large.
On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
Thus our objective is to exploit the characteristics of VM snapshot data and
pursue a cost-effective solution with the following two aspects.
First,   VM snapshot backup should only use a minimal amount of system
resource so that most of resource is allocated for regular cloud system services or applications.
Second, VM snapshot backup should be  decentralized and localized as much as possible.
That brings the benefits for increased parallelism  and fault isolation.

>>>>

Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
virtual disk image backup and even each virtual disk is viewed as a file logically, its size is very large.
On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud everyday. 
One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
resource so that most of resource is allocated for regular cloud system services or applications.
Thus our objective is to exploit the characteristics of VM snapshot data and
pursue a cost-effective deduplication solution. 
Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
which brings the benefits for increased parallelism  and fault isolation.
